\documentclass[a4paper,11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{letter}{}
\opening{Dear Mark Brereton,}

I am writing to express my interest in the Senior/Lead Java Developer contract role. With over 18 years of commercial Java experience and nearly four years of fully remote contract work, I bring a strong track record of delivering high-quality, scalable software solutions in distributed and enterprise environments. I am immediately available and well-suited to outside IR35 engagements.

In my most recent contract at Noumena Digital, I led and contributed to projects spanning financial services, blockchain, and renewable energy. These included developing a Virtual Power Plant for N-Ergie, implementing a Smart Billing Platform leveraging blockchain tokenisation, and delivering a Private Markets Exchange PoC for Julius Baer. My role combined hands-on development in Java and Kotlin with leadership responsibilities, ensuring projects were delivered on time and aligned with client requirements.

Previously, at CyberSource (Visa) and Citibank, I was responsible for architecting and implementing high-volume, low-latency systems, including payment tokenisation services and distributed stream-processing platforms. These roles required strong expertise in Java, Spring Boot, microservices, CI/CD, and cloud technologies, as well as the ability to guide small teams to success.

I am particularly drawn to this opportunity because it aligns perfectly with my experience in remote, client-facing, and delivery-focused roles. I thrive in distributed teams and am confident in my ability to contribute immediately, adding value from day one.

I would welcome the chance to discuss how my skills and background can support your team’s success. Thank you for considering my application, and I look forward to hearing from you.

\closing{Kind regards,}

\signature{Stuart Shannon}
Stuart Shannon \\
Email: \texttt{shannoncode@yahoo.com} \\
Tel: +44 (0)7834 452305 \\
LinkedIn: \texttt{linkedin.com/in/stuart-shannon-bb780530}

\end{letter}

\end{document}
